Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.

### 2022-05-02 article/draft.tex
added logo in footer
text modifications/suggestions by HT

@@

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, M\'{e}dialab SciencesPo.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{heloise.thero@sciencespo.fr, M\'{e}dialab SciencesPo.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, M\'{e}dialab SciencesPo.}}
\date{September 27, 2021}
\maketitle

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The misinformation phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society when it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|c|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API v2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API v3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Summary of ressources used for data collection.}
\label{tab1}
\end{table}

@@

More specifically, in this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube. We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ 
informing users with flags and notices, and $(iii)$ reducing the visibility of some content. We compile in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article. Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks. To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g. suspension) was announced on the social media accounts linked to a given domain name. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. 
%Thus, after manually adding this page to the CrowdTangle dashboard, 
Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} We used Minet command line tool \cite{minet} to collect the data. We can verify on figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

@@

%paragraph strike system + say following example is a manual decision. 
Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy. Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform. A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}.\footnote{See \href{https://en.wikipedia.org/wiki/Twitter\_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}
The 12-hour account lock is hard to observe in the data, 
especially for users who do not have an over the clock regular tweeting activity.\footnote{The following tool \href{https://makeadverbsgreatagain.org/allegedly/}{https://makeadverbsgreatagain.org/allegedly/} provides an overview of the daily and hourly tweeting activity, including repetition of Tweets for any given Twitter account.} 
In this section, we provide one example of a temporary suspension of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/S4}{https://open.feedback.org/media/S4}.}. We collected the activity (tweets, replies, quotes, retweets) on their Twitter account via the Twitter API, using the historical search endpoint. We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in panel $a$ of figure \ref{fig2}). The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

\begin{figure}[h]
\hspace{-2em}
%\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite_domain.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

To further assess the impact of this double temporary suspension, we collect via the Twitter API v2, all the tweets that have shared during the same period a url link containing lifesitenews.com. Panel $(b)$ of figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension. More specifically, there was an average of 960 tweets (including retweets) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 tweets (including retweets) per day during the exact same period one year earlier.

Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules. In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media articles published on their website. Panel $(b)$ points towards the limitations of suspending the Twitter account $@LifeSite$, because the 
articles published on lifesitenews.com were still being actively shared by other Twitter users.

@@

In this section, we turn to the suspension policy of YouTube. 
When a YouTube channel publishes a video that violates the community guidelines for the first time, it will usually receive a warning. 
But for the second violation, the channel receives its first strike.
A strike means that users are not allowed to post content on their YouTube channel for one week.
A strike remains associated to a channel for 90 days, and if a second strike occurs in the same 90-day period as the first strike, the suspension will then last for two weeks.
A third strike results in the termination of the channel.\footnote{https://support.google.com/youtube/answer/2802032}
To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/user/TonyHeller1}{Tony Heller}.

@@

The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/AE6Q}{https://open.feedback.org/media/AE6Q}.}  
According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
We collected the number of video uploaded and the number of view of this channel using the YouTube API v3, between November $2020$ and January $2021$. For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.
%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021.} 
\label{fb_flags}
\end{figure}
%\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .} 
No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flagging policy is thus via scraping publicly available content. To that end, we added a new feature in Minet~\cite{minet} which could automatically verify the presence or absence of flags.

We first searched for all the Facebook posts having shared a specific link rated as ‘False’ by Science Feedback, a fact-checking organization which partners with Facebook. We used the {\it search} endpoint in Minet.\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.} 
Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they contained an information banner, a fact-check flag, both or none. Three posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has informed Facebook that they have assigned the rating ``False'' for this link, we expected that all these posts would contain a fact-check flag, but we had no expectations for the information banner.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{../figure/facebook_pie_flags.png}
\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners. The claim fact checked as False appeared in the following article on beforeitsnews.com:  ``Stay Away From The Vaxxed, It Is Official, From Pfizer’s Own Documents". }
\label{tab_flags_fb}
\end{figure}

@@

We also observed that most of the posts sharing this ``False'' link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ``Visit the COVID-19 Information Centre for vaccine resources" (see the first two examples of Figure \ref{fb_flags}). We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example). It should be noted that some posts displayed both the information and the fact-check banners, as in the middle panel of Figure \ref{fb_flags}.

@@

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicates sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet without an information notice. Right Panel: Tweet containing an information notice.}
	\label{fig8}
\end{figure}

%	\caption{Two tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Right Panel: Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}

>>>>

\usepackage{url}
\usepackage{background}
\usepackage{lastpage}

\backgroundsetup{
  scale=1,
  color=black,
  opacity=1,
  angle=0,
  position=current page.south,
  vshift=60pt,
  contents={%
  \small\sffamily%
  \begin{minipage}{.18\textwidth}
  \includegraphics[width=\linewidth,height=70pt,keepaspectratio]{./img/logo.png}
  \end{minipage}\hspace{.02\textwidth}%
   \begin{minipage}{.8\textwidth}
  %\parbox[b]{.6\textwidth}{%
   % Page \thepage\ of   \pageref{LastPage}}
   \hfill
  \parbox[b]{.4\textwidth}{%
    \raggedleft Working paper, $2022$-$1$, April $2022$}\\
 % \textcolor{red}{\rule{\textwidth}{1.5pt}}\\
  %\url{www.mycompany.com}
  \end{minipage}
  }
}

@@

\title{Monitoring misinformation related interventions by Facebook, Twitter and YouTube: methods and illustration.}
\author{Shaden Shabayek\footnote{Corresponding author: shaden.shabayek@sciencespo.fr, Sciences Po, m\'{e}dialab.}, H\'{e}lo\"{i}se Th\'{e}ro\footnote{thero.heloise@gmail.com, Sciences Po, m\'{e}dialab.}, Dana Almanla\footnote{dana.almanla@cri-paris.org, CRI.}, Emmanuel Vincent\footnote{emmanuel.vincent@sciencespo.fr, Sciences Po, m\'{e}dialab.}}
\date{April 29, 2022}
\maketitle

@@

Hence, in the present article, we focus on mainstream platforms' policies and interventions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (see Lazer et al. (2018)~\cite{lazer}). The misinformation phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society when it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. The company uses a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''}} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for YouTube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see Appendix \ref{links} for references).

@@

%\begin{table}[h]
%\centering
%\begin{tabular}{|l|c|l|l|l}
%
%\hline
%&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
% \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}    
%\\ \hline
% \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API v2} & \multicolumn{1}{l|}{ \href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{minet tw scrape} }                                                                                                                                                                           \\ \hline
% \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API v3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
%\end{tabular}
%\caption{Summary of ressources used for data collection.}
%\label{tab1}
%\end{table}

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|l}
\cline{1-3}
 & {\bf Application Programming Interface (API)} & {\bf Web Scrapping}  &  \\  \cline{1-3}
\includegraphics[scale=0.035]{./img/fb_logo.png}  & \href{https://www.crowdtangle.com}{CrowdTangle API} and \href{https://buzzsumo.com}{Buzzsumo API}  & Code created for this article &  \\ \cline{1-3}
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2}  & \href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{minet tw scrape} &  \\ \cline{1-3}
 \includegraphics[scale=0.03]{./img/yt_logo.png} & \href{https://developers.google.com/youtube/v3}{YouTube API V3} & Code created for this article &  \\ \cline{1-3}
\end{tabular}
\caption{Summary of ressources used for data collection.}
\label{tab1}
\end{table}

@@

More specifically, in this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube. We classified those common policies into three broad categories: $(i)$ temporary or permanent suspension of users, $(ii)$ 
informing users with flags and notices, and $(iii)$ reducing the visibility of some content. We compile in Table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article. Furthermore, the examples provided to illustrate how to monitor a given policy were picked out of a list of domain names with several failed fact-checks. To be more precise, some domain names with failed fact-checks were picked because a given platform communicated about an intervention or because an intervention (e.g. suspension) was announced on the social media accounts linked to a given domain name. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.

@@

Facebook can also apply a temporary suspension, and in this case the data can often be collected and analyzed. For example, \href{https://www.facebook.com/DonaldTrump/}{Donald Trump’s official Facebook page}  has been suspended following the Capitol attack on January 6, 2021.\footnote{See \href{https://www.facebook.com/zuck/posts/10112681480907401}{https://www.facebook.com/zuck/posts/10112681480907401}} Nevertheless the page’s data is still present in the CrowdTangle API. 
%Thus, after manually adding this page to the CrowdTangle dashboard, 
Hence, we collected the $6$ $083$ posts it had published between January $1$, $2020$ and June $15$, $2021$ using the {\it posts} endpoint.\footnote{See the endpoint documentation for more details: \href{https://github.com/CrowdTangle/API/wiki/Posts}{https://github.com/CrowdTangle/API/wiki/Posts}.} The minet Python library\cite{minet} was used to collect the data. We can verify on Figure \ref{fig1_fb} that the {\it Donald J. Trump} page has not published any content since January $6$, 2021, and that this behavior is not consistent with the page’s previous activity: an average of $16$ posts were published each day on Facebook before the suspension.

@@

%paragraph strike system + say following example is a manual decision. 
Twitter has implemented a strike system as part of their Civic Integrity Policy and their COVID-19 misleading information policy (see Table \ref{summary} in Appendix \ref{links}). Violations of both policies can entail strikes, where two strikes lead to a 12-hour account lock and five or more strikes lead to permanent suspension from the platform. A list of notable Twitter temporary and permanent suspensions can be found on  \href{https://en.wikipedia.org/wiki/Twitter_suspensions}{Wikipedia}.\footnote{See \href{https://en.wikipedia.org/wiki/Twitter\_suspensions}{https://en.wikipedia.org/wiki/Twitter\_suspensions}.}
The 12-hour account lock is hard to observe in the data, 
especially for users who do not have an over the clock regular tweeting activity.\footnote{The following tool \href{https://makeadverbsgreatagain.org/allegedly/}{https://makeadverbsgreatagain.org/allegedly/} provides an overview of the daily and hourly tweeting activity, including repetition of Tweets for any given Twitter account.} 
In this section, we provide one example of a temporary suspension of a Twitter account, that seems to be the result of a manual decision concerning a Tweet which violated the rules.

The Twitter account $@LifeSite$ of the website lifesitenews.com has been suspended for at least two periods of time: from end of 2019 until fall 2020 for 308 days, then again since January 2021 for having violated Twitter Rules\footnote{See Lifesitenews's article discussing the reason for the suspension: \href{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}{https://www.lifesitenews.com/news/lifesite-is-dumping-twitter-and-so-should-you}. Twitter rules can be found at: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{https://help.twitter.com/en/rules-and-policies/twitter-rules}. }. In particular, this website has several failed fact-checks concerning the published articles, according to Media Bias Fact Check and open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/life-site-news/}{https://mediabiasfactcheck.com/life-site-news/} and \href{https://open.feedback.org/media/CM}{https://open.feedback.org/media/CM}.}. We collected the activity (Tweets, Replies, Quotes, Retweets) on their Twitter account via the Twitter API, using the historical search endpoint. We then plotted the number of Tweets, Retweets, Quotes and Replies per day, as shown in the left panel of Figure \ref{fig2}. The two periods of temporary suspension are clearly observed in the data as the user(s) of the account were not allowed to use the functionalities of the Twitter Platform.

\begin{figure}[h]
\hspace{-2em}
%\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite_updated_legend.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.32]{../figure/lifesite_domain_updated_legend.jpg}
	%\end{multicols}
\caption{Left Panel: number of Tweets (including Retweets, Replies, Quotes) per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Right Panel: number of Tweets (including Retweets, Replies, Quotes) per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

To further assess the impact of this double temporary suspension, we collect via the Twitter API v2, all the Tweets that have shared during the same period a url link containing lifesitenews.com. The right panel of Figure \ref{fig2}, shows that during both periods of temporary suspension, other users still shared lifesitenews.com links and that the level was only slightly below the tweeting and retweeting levels prior to the first temporary suspension. More specifically, there was an average of 960 Tweets (including Retweets, Replies, Quotes) per day over the first temporary suspension period of 308 days from December 9, 2019 until October 12, 2020, against an average of 977 Tweets (including Retweets, Replies, Quotes) per day during the exact same period one year earlier.

Finally, suspending a Twitter account is an intervention which aims at penalizing users, in order to make them respect the Twitter rules. In the case of Twitter accounts linked to domain names, the activity of the account usually consists in spreading on social media articles published on their website. The right panel of Figure \ref{fig2} points towards the limitations of suspending the Twitter account $@LifeSite$, because the 
articles published on lifesitenews.com were still being actively shared by other Twitter users.

@@

In this section, we turn to the suspension policy of YouTube. 
When a YouTube channel publishes a video that violates the community guidelines for the first time, it will usually receive a warning. 
But for the second violation, the channel receives its first strike.
A strike means that users are not allowed to post content on their YouTube channel for one week.
A strike remains associated to a channel for 90 days, and if a second strike occurs in the same 90-day period as the first strike, the suspension will then last for two weeks.
A third strike results in the termination of the channel.\footnote{\href{https://support.google.com/youtube/answer/2802032}{https://support.google.com/youtube/answer/2802032}.}
To illustrate the implementation of this policy, we use the following YouTube channels as two examples of  one-week suspensions: \href{https://www.youtube.com/channel/UCNbIDJNNgaRrXOD7VllIMRQ}{One America news Network} and \href{https://www.youtube.com/channel/UCprclkVrNPls7PR-nHhf1Ow}{Tony Heller}.

@@

The website of One America News Network has a ``low'' factual reporting score according to the website Media Bias Fact Check and several inaccurate articles according to open.feedback.org.\footnote{See \href{https://mediabiasfactcheck.com/one-america-news-network/}{mediabiasfactcheck.com/one-america-news-network/} and \href{https://open.feedback.org/media/5M}{https://open.feedback.org/media/5M}.}  
According to NBC news (2020)~\cite{nbcnews}, the YouTube channel received a first strike on November $24$, $2020$ for the promotion of a false cure for COVID-19.
We collected the number of video uploaded and the number of view of this channel using the YouTube API v3, between November $2020$ and January $2021$. For the video counts, we used the {\it playlists} endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists, then via the {\it videos} endpoint we retrieved the view counts on June $2021$.
%\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021.} 
\label{fb_flags}
\end{figure}
%\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/} \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{3835629366473816} .} 
No information or available fields regarding the Facebook flags can be found on Buzzsumo or CrowdTangle, the two APIs we use to access Facebook data. The only way to verify Facebook’s flagging policy is thus via scraping publicly available content.

We first searched for all the Facebook posts having shared a specific link\footnote{ Click \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{here} to access the link and  \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{its fact-check by Health Feedback}.} rated as ‘False’ by Science Feedback, a fact-checking organization which partners with Facebook. To do so, we used the `search' endpoint in CrowdTangle API.
Twenty Facebook posts were collected this way, and we scripted an adapted scraping code to verify whether they contained an information banner, a fact-check flag, both or none. Three posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has informed Facebook that they have assigned the rating ``False'' for this link, we expected that all these posts would contain a fact-check flag, but we had no expectations for the information banner.

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.4]{../figure/facebook_pie_flags_updated.png}
\caption{Count of different flags for 17 Facebook posts who have shared the exact same link, fact-checked False by one of Facebook’s partners. }
\label{tab_flags_fb}
\end{figure}

@@

We also observed that most of the posts sharing this ``False'' link (13 out of 17, Figure \ref{tab_flags_fb}) had an information banner saying ``Visit the COVID-19 Information Centre for vaccine resources" (see the first two examples of Figure \ref{fb_flags}). We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example). It should be noted that some posts displayed both the information and the fact-check banners, as in the middle panel of Figure \ref{fb_flags}.

@@

Alongside other social networking platforms, when the content of a Tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center. At the Tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID-19 or presidential elections) and  redirect users to a webpage to get more context, for example {\it ``Get the facts about COVID-19''} (see right panel of Figure \ref{fig8}). Interstitials are presented as a greyed box on top of a Tweet, which indicates sensitive content, violations of Twitter rules, withheld Tweets for violation of local laws or even Tweets from suspended accounts, for example {\it ``The following media includes potentially sensitive content''} (see left panel of Figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

@@

\begin{figure}[h]
\centering
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	\caption{Two Tweets sharing the same link marked as ``False'' by Science Feedback, screenshots taken on June $20$, 2021. Left Panel: Tweet without an information notice. Right Panel: Tweet containing an information notice.}
	\label{fig8}
\end{figure}
